Towards open collaboration in biomedical and health research: A scoping review

### 2022-09-02 doc/protocol.Rmd
my affiliations

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Luke W. Johnston
    affiliation: 1
  - name: Daniel Ibsen
    affiliation: 1
  - name: Hannah Chatwin
    affiliation: 1
  - name: Mario Garcia
    affiliation: 1
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: 
output: prereg::prereg_pdf
---

>>>>

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Luke W. Johnston
    affiliation: "1,2"
  - name: Daniel Ibsen
    affiliation: 1
  - name: Hannah Chatwin
    affiliation: 1
  - name: Mario Garcia
    affiliation: 1
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: Aarhus University, Denmark
output: prereg::prereg_pdf
---
